Some title

### 2017-12-07 tex/neural_network.tex
Small changes in tex, not visible

\newcommand{\nnfontsize}{\tiny}

\centering
\begin{tikzpicture}[node distance=1.2cm, >=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left:\nnfontsize State (12)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above:\nnfontsize Linear}] {};

@@

    \node [lstm place] (s3) [right of=s2, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [lstm place] (s4) [right of=s3, label={[align=center]below:\nnfontsize LSTM (32)}] {};

@@

    \node [softplus place] (s7) [right of=s4, label={[align=center]below:{\nnfontsize Softplus}}] {};

@@

    \node [output place] (s8) [right of=s7, label={[align=center]below:\nnfontsize $\sigma$~(1)}] {};

@@

    \node [place] (s5) [above of=s7, label={[align=center]above:\nnfontsize Linear}] {};

@@

    \node [output place] (s6) [right of=s5, label={[align=center]above:\nnfontsize $\mu$ (1)}] {};

@@

    \node [place] (s10) [below right of=s1, label={[align=center]below:\nnfontsize Linear}] {};

@@

    \node [lstm place] (s11) [right of=s10, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [lstm place] (s12) [right of=s11, label={[align=center]above:\nnfontsize LSTM (32)}] {};

@@

    \node [softplus place] (s13) [right of=s12, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above:\nnfontsize $V_\text{packets}$ (1)}] {};

@@

    \node [softplus place] (s15) [below of=s13, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s19) [right of=s15, label={[align=center]above:\nnfontsize $V_\text{delay}$ (1)}] {};

@@

    \node [softplus place] (s16) [below of=s15, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]above:\nnfontsize $V_\text{lost}$ (1)}] {};

@@

    \node [softplus place] (s14) [below of=s16, label={[align=center]above:\nnfontsize Softplus}] {};

@@

    \node [output place] (s21) [right of=s14, label={[align=center]above:\nnfontsize $V_\text{duration}$ (1)}] {};

@@

%    \node [softplus place] (s17) [below of=s14, label={[align=center]above:\nnfontsize Softplus}] {};
%    
%  \path[->] (s12) edge node {} (s17);
%    
%    \node [output place] (s22) [right of=s17, label={[align=center]above:\nnfontsize $V_\text{byte}$ (1)}] {};   
%    
%  \path[->] (s17) edge node {} (s22);

>>>>

\centering
\begin{tikzpicture}[every label/.append style={font=\tiny}, node distance=1.2cm, >=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [input place] (s1) [label={[align=center]left: State (12)}] {};
    \node [place] (s2) [above right of=s1, label={[align=center]above: Linear}] {};

@@

    \node [lstm place] (s3) [right of=s2, label={[align=center]below: LSTM (32)}] {};

@@

    \node [lstm place] (s4) [right of=s3, label={[align=center]below: LSTM (32)}] {};

@@

    \node [softplus place] (s7) [right of=s4, label={[align=center]below:{ Softplus}}] {};

@@

    \node [output place] (s8) [right of=s7, label={[align=center]below: $\sigma$~(1)}] {};

@@

    \node [place] (s5) [above of=s7, label={[align=center]above: Linear}] {};

@@

    \node [output place] (s6) [right of=s5, label={[align=center]above: $\mu$ (1)}] {};

@@

    \node [place] (s10) [below right of=s1, label={[align=center]below: Linear}] {};

@@

    \node [lstm place] (s11) [right of=s10, label={[align=center]above: LSTM (32)}] {};

@@

    \node [lstm place] (s12) [right of=s11, label={[align=center]above: LSTM (32)}] {};

@@

    \node [softplus place] (s13) [right of=s12, label={[align=center]above: Softplus}] {};

@@

    \node [output place] (s17) [right of=s13, label={[align=center]above: $V_\text{packets}$ (1)}] {};

@@

    \node [softplus place] (s15) [below of=s13, label={[align=center]above: Softplus}] {};

@@

    \node [output place] (s19) [right of=s15, label={[align=center]above: $V_\text{delay}$ (1)}] {};

@@

    \node [softplus place] (s16) [below of=s15, label={[align=center]above: Softplus}] {};

@@

    \node [output place] (s20) [right of=s16, label={[align=center]above: $V_\text{lost}$ (1)}] {};

@@

    \node [softplus place] (s14) [below of=s16, label={[align=center]above: Softplus}] {};

@@

    \node [output place] (s21) [right of=s14, label={[align=center]above: $V_\text{duration}$ (1)}] {};

@@

%    \node [softplus place] (s17) [below of=s14, label={[align=center]above: Softplus}] {};
%    
%  \path[->] (s12) edge node {} (s17);
%    
%    \node [output place] (s22) [right of=s17, label={[align=center]above: $V_\text{byte}$ (1)}] {};   
%    
%  \path[->] (s17) edge node {} (s22);

### 2017-12-07 tex/petri_net.tex
Small changes in tex, not visible

\newcommand{\nodedistance}{2}
\newcommand{\nd}[1]{\numexpr #1 * \nodedistance \relax}

\centering
\begin{tikzpicture}[node distance=\nodedistance,>=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [place,tokens=1] (s1) at (\nd{0}, \nd{1}) [label={[align=center]left:Receive\\ feedback}] {};
    \node [place] (s2) at (\nd{1}, \nd{2}) [label={[align=center]above:Received\\ ACK}] {};
    \node [place] (s3) at (\nd{2}, \nd{1}) [label={[align=center]right:Packets\\ in the\\ network}] {};
    \node [place] (s4) at (\nd{1}, \nd{0}) [label={[align=center]below:Open congestion\\ window (cwnd)}] {};

    \node [transition] (e1) at (\nd{0}, \nd{0}) [label=left:Take action] {}
      edge [post] node {$a$}(s4)
      edge [pre] node {1} (s1);

    \node [transition] (e2) at (\nd{2}, \nd{0}) [label={[align=center]right:Send\\ packet}] {}
      edge [pre] node {1} (s4)
      edge [post] node {1} (s3);

    \node [transition] (e3) at (\nd{2}, \nd{2}) [label={[align=center]right:Receive\\ ACK}] {}
      edge [pre] node {1} (s3)
      edge [post] node {1} (s2);

    \node [transition] (e4) at (\nd{1}, \nd{1}) [label={[align=center]left:Update\\open\\cwnd}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s4);

    \node [transition] (e5) at (\nd{0}, \nd{2}) [label={[align=center]left:Received\\ feedback}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s1);

>>>>

\centering
\begin{tikzpicture}[x=2cm,y=2cm,>=stealth',bend angle=45,auto]

@@

  \begin{scope}
    \node [place,tokens=1] (s1) at (0, 1) [label={[align=center]left:Receive\\ feedback}] {};
    \node [place] (s2) at (1, 2) [label={[align=center]above:Received\\ ACK}] {};
    \node [place] (s3) at (2, 1) [label={[align=center]right:Packets\\ in the\\ network}] {};
    \node [place] (s4) at (1, 0) [label={[align=center]below:Open congestion\\ window (cwnd)}] {};

    \node [transition] (e1) at (0, 0) [label=left:Take action] {}
      edge [post] node {$a$}(s4)
      edge [pre] node {1} (s1);

    \node [transition] (e2) at (2, 0) [label={[align=center]right:Send\\ packet}] {}
      edge [pre] node {1} (s4)
      edge [post] node {1} (s3);

    \node [transition] (e3) at (2, 2) [label={[align=center]right:Receive\\ ACK}] {}
      edge [pre] node {1} (s3)
      edge [post] node {1} (s2);

    \node [transition] (e4) at (1, 1) [label={[align=center]left:Update\\open\\cwnd}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s4);

    \node [transition] (e5) at (0, 2) [label={[align=center]left:Received\\ feedback}] {}
      edge [pre] node {1} (s2)
      edge [post] node {1} (s1);
